---
title: "capstone_model_3_2 (hier)"
output: pdf_document
date: "2022-12-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Helper packages

```{r}
library(dplyr)       # for data manipulation
library(ggplot2)     # for data visualization
```

# Modeling packages
```{r}
library(cluster)     # for general clustering algorithms
library(factoextra)  # for visualizing cluster results
```
#import dataset
```{r, eval = FALSE}
radiomics <- read.csv("radiomics_completedata.csv")
```

```{r, eval = FALSE}
str(radiomics)
glimpse(radiomics)

# initial dimension
dim(radiomics)


#check for missing values
is.na(radiomics)
sum(is.na(radiomics))
na.omit(radiomics)
```


# Scale data
```{r, eval = FALSE}
scale(radiomics)
head(radiomics)
newdf1 = subset(radiomics, select = c(-Institution))
newdf1
```

```{r, eval = FALSE}
#Determining Optimal Number of Clusters
set.seed(123)
```
# Dissimilarity matrix
```{r, eval = FALSE}
d <- dist(newdf1, method = "euclidean")
```
# Hierarchical clustering using Complete Linkage
```{r, eval = FALSE}
hc1 <- hclust(d, method = "complete" )
```
# For reproducibility
```{r, eval = FALSE}
set.seed(123)
```
# Compute maximum or complete linkage clustering with agnes
```{r, eval = FALSE}
hc2 <- agnes(newdf1, method = "complete")
```
# Agglomerative coefficient
```{r, eval = FALSE}
hc2$ac
## [1] 0.926775
```
# methods to assess
```{r, eval = FALSE}
m <- c( "average", "single", "complete", "ward")
names(m) <- c( "average", "single", "complete", "ward")
```
# function to compute coefficient
```{r, eval = FALSE}
ac <- function(x) {
  agnes(newdf1, method = x)$ac
}
```
# get agglomerative coefficient for each linkage method
```{r, eval = FALSE}
purrr::map_dbl(m, ac)
##   average    single  complete      ward 
## 0.9139303 0.8712890 0.9267750 0.9766577
```
# compute divisive hierarchical clustering
```{r, eval = FALSE}
hc4 <- diana(newdf1)
```
# Divise coefficient; amount of clustering structure found
```{r, eval = FALSE}
hc4$dc
## [1] 0.9191094
```
# Plot cluster results
```{r, eval = FALSE}
p1 <- fviz_nbclust(newdf1, FUN = hcut, method = "wss", 
                   k.max = 10) +
  ggtitle("(A) Elbow method")
p2 <- fviz_nbclust(newdf1, FUN = hcut, method = "silhouette", 
                   k.max = 10) +
  ggtitle("(B) Silhouette method")
p3 <- fviz_nbclust(newdf1, FUN = hcut, method = "gap_stat", 
                   k.max = 10) +
  ggtitle("(C) Gap statistic")
```
# Display plots side by side
```{r, eval = FALSE}
gridExtra::grid.arrange(p1, p2, p3, nrow = 1)
```
# Construct dendorgram  
```{r, eval = FALSE}
hc5 <- hclust(d, method = "ward.D2" )
dend_plot <- fviz_dend(hc5)
dend_data <- attr(dend_plot, "dendrogram")
dend_cuts <- cut(dend_data, h = 8)
fviz_dend(dend_cuts$lower[[2]])
```
# Ward's method
```{r, eval = FALSE}
hc5 <- hclust(d, method = "ward.D2" )
```
# Cut tree into 4 groups
```{r, eval = FALSE}
sub_grp <- cutree(hc5, k = 8)
```
# Number of members in each cluster
```{r, eval = FALSE}
table(sub_grp)
```
# Plot full dendogram
```{r, eval = FALSE}
fviz_dend(
  hc5,
  k = 8,
  horiz = TRUE,
  rect = TRUE,
  rect_fill = TRUE,
  rect_border = "jco",
  k_colors = "jco",
  cex = 0.1
)


dend_plot <- fviz_dend(hc5)                # create full dendogram
dend_data <- attr(dend_plot, "dendrogram") # extract plot info
dend_cuts <- cut(dend_data, h = 70.5)      # cut the dendogram at designated height
# Create sub dendrogram plots
p1 <- fviz_dend(dend_cuts$lower[[1]])
p2 <- fviz_dend(dend_cuts$lower[[1]], type = 'circular')
```
# Side by side plots
```{r, eval = FALSE}
gridExtra::grid.arrange(p1, p2, nrow = 1)
```









